cardinalR: Generating interesting high-dimensional data structures

### 2025-04-30 paper-cardinalR.Rmd
Fixed the issue fo Figure 2

```{r layouts}
clusters <- five_clusts |> pull(cluster)

tsne_data <- read_rds("data/five_clusts/five_clusts_tsne_perplexity_30.rds") |>
  mutate(cluster = clusters)

@@

umap_data <- read_rds("data/five_clusts/five_clusts_umap_n-neigbors_15_min-dist_0.1.rds") |>
  mutate(cluster = clusters)

@@

phate_data <- read_rds("data/five_clusts/five_clusts_phate_knn_5.rds") |>
  mutate(cluster = clusters)

@@

trimap_data <- read_rds("data/five_clusts/five_clusts_trimap_n-inliers_12_n-outliers_4_n-random_3.rds") |>
  mutate(cluster = clusters)

@@

pacmap_data <- read_rds("data/five_clusts/five_clusts_pacmap_n-neighbors_10_init_random_MN-ratio_0.5_FP-ratio_2.rds") |>
  mutate(cluster = clusters)

@@

pca_data <- read_rds("data/five_clusts/five_clusts_pca.rds") |>
  mutate(cluster = clusters)

@@

>>>>

```{r layouts}

tsne_data <- read_rds("data/five_clusts/five_clusts_tsne_perplexity_30.rds")

@@

umap_data <- read_rds("data/five_clusts/five_clusts_umap_n-neigbors_15_min-dist_0.1.rds")

@@

phate_data <- read_rds("data/five_clusts/five_clusts_phate_knn_5.rds")

@@

trimap_data <- read_rds("data/five_clusts/five_clusts_trimap_n-inliers_12_n-outliers_4_n-random_3.rds")

@@

pacmap_data <- read_rds("data/five_clusts/five_clusts_pacmap_n-neighbors_10_init_random_MN-ratio_0.5_FP-ratio_2.rds")

@@

pca_data <- read_rds("data/five_clusts/five_clusts_pca.rds")

@@

- Branching: These functions create a controlled environment for testing how effectively various algorithms preserve branching topology and continuity in their low-dimensional embeddings.
